[1] Dubois, D. and H. Prade, Fuzzy Sets and Systems: Theory and Applications, Academic Press, New York, 1980.

[2] Kaufmann, A. and M.M. Gupta, Introduction to Fuzzy Arithmetic, V.N. Reinhold, 1985.

[3] Lee, C.-C., "Fuzzy logic in control systems: fuzzy logic controller-parts 1 and 2," IEEE Transactions on Systems, Man, and Cybernetics, Vol. 20, No. 2, pp 404-435, 1990.

[4] Mamdani, E.H. and S. Assilian, "An experiment in linguistic synthesis with a fuzzy logic controller," International Journal of Man-Machine Studies, Vol. 7, No. 1, pp. 1-13, 1975.

[5] Mamdani, E.H., "Advances in the linguistic synthesis of fuzzy controllers," International Journal of Man-Machine Studies, Vol. 8, pp. 669-678, 1976.

[6] Mamdani, E.H., "Applications of fuzzy logic to approximate reasoning using linguistic synthesis," IEEE Transactions on Computers, Vol. 26, No. 12, pp. 1182-1191, 1977.

[7] Schweizer, B. and A. Sklar, "Associative functions and abstract semi-groups," Publ. Math Debrecen, 10:69-81, 1963.

[8] Sugeno, M., "Fuzzy measures and fuzzy integrals: a survey," (M.M. Gupta, G. N. Saridis, and B.R. Gaines, editors) Fuzzy Automata and Decision Processes, pp. 89-102, North-Holland, NY, 1977.

[9] Sugeno, M., Industrial applications of fuzzy control, Elsevier Science Pub. Co., 1985.

[10] Yager, R., "On a general class of fuzzy connectives," Fuzzy Sets and Systems, 4:235-242, 1980.

[11] Yager, R. and D. Filev, "Generation of Fuzzy Rules by Mountain Clustering," Journal of Intelligent & Fuzzy Systems, Vol. 2, No. 3, pp. 209-219, 1994.

[12] Zadeh, L.A., "Fuzzy sets," Information and Control, Vol. 8, pp. 338-353, 1965.

[13] Zadeh, L.A., "Outline of a new approach to the analysis of complex systems and decision processes," IEEE Transactions on Systems, Man, and Cybernetics, Vol. 3, No. 1, pp. 28-44, Jan. 1973.

[14] Zadeh, L.A., "The concept of a linguistic variable and its application to approximate reasoning, Parts 1, 2, and 3," Information Sciences, 1975, 8:199-249, 8:301-357, 9:43-80.

[15] Zadeh, L.A., "Fuzzy Logic," Computer, Vol. 1, No. 4, pp. 83-93, 1988.

[16] Zadeh, L.A., "Knowledge representation in fuzzy logic," IEEE Transactions on Knowledge and Data Engineering, Vol. 1, pp. 89-100, 1989